Estimation of COVID-19 cases in Ontario

### 2022-03-31 outputs/paper/paper.Rmd
initial submission

---
title: "Estimation of COVID-19 cases in Ontario"
author:
- Zihan Zhang
thanks: "Code and data are available at: https://github.com/zihanjasmine/final-paper."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "COVID-19 is a respiratory disease first discovered in 2019 and then spread across the world. Many people may be facing an increased level of anxiety and stress. In this report, we built a poisson model to estimate the COVID 19 cases in Ontario. We focus on how gender and age group affect the probability of getting COVID-19."
Keywords: COVID-19, logistic model
output:
  bookdown::pdf_document2
bibliography: references.bib
---

@@

>>>>

---
title: "Estimation of COVID-19 cases in Ontario"
author:
- Zihan Zhang
thanks: "Code and data are available at: https://github.com/zihanjasmine/Estimation-of-COVID-19-cases-in-Ontario."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "COVID-19 is a respiratory disease first discovered in 2019 and then spread across the world. Many people may be facing an increased level of anxiety and stress. In this report, we built a poisson model to estimate the COVID 19 cases in Ontario. We focus on how gender and age group affect the probability of getting COVID-19."
Keywords: COVID-19, logistic model
output:
  bookdown::pdf_document2
bibliography: references.bib
---

@@

Mortality analyses. Johns Hopkins Coronavirus Resource Center. (n.d.). Retrieved March 31, 2022, from https://coronavirus.jhu.edu/data/mortality

World Health Organization. (n.d.). Coronavirus. World Health Organization. Retrieved March 31, 2022, from https://www.who.int/health-topics/coronavirus#tab=tab_1
